Untitled

### 2023-10-28 code/analysis_Redo.Rmd
test
adding digits

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no") %>% 
  add_p()

>>>>

dfc %>% 
  filter(Year == 2010) %>% 
  mutate(Treat = ifelse(Att > 0, "Treated", "Control")) %>% 
  select(Treat, Total, Pct.NHA:Pct.COM) %>% 
  #filter(!complete.cases(.)) %>% 
  tbl_summary(by = Treat, 
                statistic = list(all_continuous() ~ "{mean} ({sd})"),
missing = "no", digits = list(everything() ~ c(2))) %>% 
  add_p(pvalue_fun = function(x) style_pvalue(x, digits = 3))
